\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-03-18 docs/parco13/abstract.tex
Typo
Beef up figure

\begin{figure}
\centering
\includegraphics[width=.4\columnwidth]{../figs_misc/cubed3}
\caption{The leaves in a forest of six octrees that serves as the computational
domain for the cubed sphere.  An adhoc refinement pattern has been 2:1 balanced
in terms of neighbor sizes and partitioned between five MPI processes (the
three middle ones are shown from black to white).}
\label{cubed3}
\end{figure}

@@

For hyperbolic problems, we integrate the solution on a single uniform patch,
containing $m^d$ cells, using the wave propagation algorithm described by R. J.
LeVeque \cite{LeVeque:1997eg} and implemented in \clawpack \cite{le:2002,
clawpack}.  We assume a single degree of freedom per cell and reconstruct a
piecewise constant solution to obtain left and right states at cell edges.  At
each edge, we solve Riemann problems to obtain left and right going waves
propagating at speeds determined from the solution to the Riemann problem.  For
scalar advection, the speed of each wave is simply the local advection speed at
the cell interface.  For non- linear problems and systems, an approximate
Riemann solver, such as a Roe solver \cite{roesolver}, is typically used.  Since
much of the physics of an application can be contained in the Riemann solver,
\forestclaw adopts \clawpack's interface to Riemann solvers effectively allowing
problems solved with \clawpack to be solvable in \forestclaw.  In order to
achieve second order accuracy wave limiters are used to suppress spurious
oscillations at sharp gradients in the flow.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=.4\columnwidth]{../figs_misc/forest_stacked}
\hspace{.05\columnwidth}
\includegraphics[width=.4\columnwidth]{../figs_misc/cubed3}
\end{center}
\caption{Left: Forest of two quadtrees, partitioned among three MPI processes.
Each quadtree has its own coordinate orientation.  The situation in 3D
(octrees) is analogous.  Right: The leaves in a forest of six quadtrees that
serves as the computational domain for the cubed sphere.  An adhoc refinement
pattern has been 2:1 balanced in terms of neighbor sizes and partitioned
between five MPI processes (the three middle ones are shown from black to
white).}
\label{cubed3}
\end{figure}

@@

For hyperbolic problems, we integrate the solution on a single uniform patch,
containing $m^d$ cells, using the wave propagation algorithm described by R. J.
LeVeque \cite{LeVeque:1997eg} and implemented in \clawpack \cite{le:2002,
clawpack}.  We assume a single degree of freedom per cell and reconstruct a
piecewise constant solution to obtain left and right states at cell edges.  At
each edge, we solve Riemann problems to obtain left and right going waves
propagating at speeds determined from the solution to the Riemann problem.  For
scalar advection, the speed of each wave is simply the local advection speed at
the cell interface.  For non-linear problems and systems, an approximate
Riemann solver, such as a Roe solver \cite{roesolver}, is typically used.  Since
much of the physics of an application can be contained in the Riemann solver,
\forestclaw adopts \clawpack's interface to Riemann solvers effectively allowing
problems solved with \clawpack to be solvable in \forestclaw.  In order to
achieve second order accuracy wave limiters are used to suppress spurious
oscillations at sharp gradients in the flow.
